Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2019-12-05 ms/spaceness.tex
put caveat on run length back in

Any simulation of a population of reproducing organisms
requires some kind of control on population sizes,
or else the population will either die out or grow very large. \llabel{demog_disco}
The usual choice of population regulation for population genetics --
a constant size, as in the Wright--Fisher model --
implies biologically unrealistic interactions between geographically distant parts of the species range.
Our choice to regulate population size by including a local density-dependent control on mortality
is only one of many possible ways to do this.
We could have instead regulated fecundity, or recruitment, or both;
this general class of models
is sometimes referred to as the ``Bolker--Pacala model'' \citep{bolker1997using}.
It is not currently clear how much different choices of demographic parameters,
or of functional forms for the regulation,
might quantitatively affect our results,
although the general predictions should be robust to similar forms of regulation.
Since populations are still entirely \emph{intrinsically} regulated,
our model still has a very strong ``population genetics'' flavor.
Alternatively, population size could be regulated by interactions with other species
(e.g., a Lotka-Volterra model),
or extrinsically specified by local resource availability
(e.g., by food or nest site availability).
Indeed, our model could be interpreted as a caricature of such a model:
as local density increases, good habitat is increasingly occupied,
pushing individuals into more marginal habitat and increasing their mortality.
Many such models should behave similarly to ours,
but others (especially those with local population cycling), may differ dramatically.
There is a clear need for greater exploration of 
the consequences for population genetics of ecologically realistic population models.

>>>>

Any simulation of a population of reproducing organisms
requires some kind of control on population sizes,
or else the population will either die out or grow very large after a sufficiently long period of time. \llabel{demog_disco}
The usual choice of population regulation for population genetics --
a constant size, as in the Wright--Fisher model --
implies biologically unrealistic interactions between geographically distant parts of the species range.
Our choice to regulate population size by including a local density-dependent control on mortality
is only one of many possible ways to do this.
We could have instead regulated fecundity, or recruitment, or both;
this general class of models
is sometimes referred to as the ``Bolker--Pacala model'' \citep{bolker1997using}.
It is not currently clear how much different choices of demographic parameters,
or of functional forms for the regulation,
might quantitatively affect our results,
although the general predictions should be robust to similar forms of regulation.
Since populations are still entirely \emph{intrinsically} regulated,
our model still has a very strong ``population genetics'' flavor.
Alternatively, population size could be regulated by interactions with other species
(e.g., a Lotka-Volterra model),
or extrinsically specified by local resource availability
(e.g., by food or nest site availability).
Indeed, our model could be interpreted as a caricature of such a model:
as local density increases, good habitat is increasingly occupied,
pushing individuals into more marginal habitat and increasing their mortality.
Many such models should behave similarly to ours,
but others (especially those with local population cycling), may differ dramatically.
There is a clear need for greater exploration of 
the consequences for population genetics of ecologically realistic population models.
